\documentclass[12pt]{report}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[tmargin=2cm, lmargin=4cm, rmargin=2.5cm, bmargin=4cm, paperwidth=8.267in, paperheight=11.692in]{geometry}
\usepackage{amsfonts}
\usepackage{array}
\usepackage{indentfirst}
\graphicspath{ {images/} }
\usepackage{lipsum}
\usepackage{verbatim}
\usepackage{titlepic}
\usepackage{nopageno}
\usepackage{amsmath}

\begin{document}
\noindent To whom it may concern,
\\ \\
My name is Carson. I live in Scotland where I'm pursuing a PhD in robotics and graphics, with a focus on novel applications and acquirement of light fields. If given the opportunity, I would happily come back for an internship at JPL for the summer as, like so many, I'm enamoured with the work being done there. Before my PhD started, I earned a MRes in the field of robotics. Before that, a BSc in Aerospace Engineering. And before that I grew up on a cattle ranch in California and worked on cars in my free time. It's been quite a journey.
\\ \\ 
I'm a down to earth dreamer. To me, this means I set my sights, sometimes on things that may seem unreasonable to some, and make them reality. I understand "big picture thinking", the concept of the devil residing in the details, and the always hard to admit "perfect is the enemy of good enough" in some situations. I enjoy a riveting puzzle, and can confidently work my way through complex debugging or deciphering of previously written code. I believe I am not a typical potential intern, and I suspect atypical is what JPL is looking for.
\\ \\
Thank you for taking the time to read this,
\\ \\
Carson Vogt
\end{document}