%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\newsectionwidth{0pt} % Stops section indenting


\begin{document}
%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{\LARGE{Carson Vogt} \\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{{\bf address} 7/9 Slateford Road, EH11 1PA, Edinburgh, UK \\{\bf skype} carson.vogt}
\address{{\bf e-mail} crvogt26@gmail.com \\ {\bf phone} +44 7713 666479} % Your address 1

%----------------------------------------------------------------------------------------

\begin{resume}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION} 

 % Gap between title and text
{\sl PhD}, Electrical Engineering (focus on graphics), Heriot-Watt University, December 2018\\
\emph{MSc by Research}, Robotics, University of Edinburgh, 2015\\ 
\emph{BSc}, Aerospace Engineering, University of Southern California, 2014 

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{EXPERIENCE}

{\sl Naval Research Enterprise Internship Program (NREIP)} \hfill June -- August 2014, June -- August 2013 \\
Naval Postgraduate School, Monterey, CA
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Worked on embedded, open source systems for UAVs to be used in swarm manoeuvres.  
\end{itemize}

{\sl The Systems Integration Organization (SI Org)}
\hfill June 2012 -- August 2012 \\
King of Prussia, PA 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Part of the Aerospace and Integration team, uncovered and deciphered MATLAB tools and learned to diagnose satellite issues.
\end{itemize} 

{\sl Vandenberg Air Force Base} 
\hfill June 2011 -- December 2011 \\ 
Lompoc, CA
\begin{itemize}\itemsep -2pt
\item Characterized ground-based sensors for Space Situational Awareness group.
\item Began development of a program to make observation abilities apparent to new users.
\end{itemize}

{\sl Information Sciences Institute (ISI)} \hfill May 2009 -- April 2012 \\
Space Engineering Research Center, Marina del Rey 
\begin{itemize}\itemsep -2pt
\item Was part of the team that helped to create the Caerus portion of the Mayflower-Caerus 3U CubeSat and the Aeneas CubeSat.
\item Team lead for LEAPFROG lunar lander avionics group.
\end{itemize}
%----------------------------------------------------------------------------------------
\section{TECHNICAL SKILLS}
\begin{itemize} \itemsep -2pt
\item Proficient in: C++, SolidWorks, Excel, electronics (including soldering), genetic algorithms, Gaussian processes, microcontrollers
\item Working Knowledge of: XFoil, composites, MATLAB, Python, ActionScript, MXML, general machine learning, computer vision
\end{itemize}

\section{POSTGRADUATE RESEARCH}
{\sl MSc Research}
\begin{itemize} \itemsep -2pt
\item Built an autonomous powered glider to take atmospheric data for wind farm optimization.
\item Utilized Gaussian processes to predict local, small-scale weather patterns.
\item Designed to fill in for relatively low resolution satellite and weather station data.
\end{itemize}
{\sl PhD Research}
\begin{itemize} \itemsep -2pt
\item Ongoing light field research for scientific applications
\item Utilizing novel data collection and interpolation methods.
\end{itemize}
\section{GENERAL INTERESTS}
\begin{itemize} \itemsep -2pt
\item Avid drone racer and exploratory drone creator/operator, both fixed wing and multirotor. 
\item Constructed an automated greenhouse indoors using RPI and Arduino.
\item Dedicated off-roader, expeditioner, and overlander, be it by Jeep or fat bike.
\item Grew up riding horses and took up polo while living in Edinburgh. etc...
\end{itemize}

%----------------------------------------------------------------------------------------

\end{resume} 
\end{document}