%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\newsectionwidth{0pt} % Stops section indenting


\begin{document}
%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{\LARGE{Carson Vogt} \\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{{\bf address} 7/9 Slateford Road, EH11 1PA, Edinburgh, UK \\{\bf skype} carson.vogt}
\address{{\bf e-mail} crvogt26@gmail.com \\ {\bf phone} +44 7713 666479} % Your address 1

%----------------------------------------------------------------------------------------

\begin{resume}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION} 

 % Gap between title and text
{\sl PhD}, Electrical Engineering (focus on graphics), Heriot-Watt University, December 2019\\
\emph{MSc by Research}, Robotics, University of Edinburgh, 2015\\ 
\emph{BSc}, Aerospace Engineering, University of Southern California, 2014 

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{EXPERIENCE}

\textbf{Naval Research Intern (NREIP)} \hfill June --August 2017, June -- August 2014, June -- August 2013 \\
Naval Postgraduate School, Monterey, CA
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Worked on embedded, open source systems for UAVs to be used in swarm manoeuvres.  
\end{itemize}
\vspace*{-\baselineskip}

\textbf{The Systems Integration Organization (SI Org)}
\hfill June 2012 -- August 2012 \\
King of Prussia, PA 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Part of the Aerospace and Integration team, uncovered and deciphered MATLAB tools and learned to diagnose satellite issues.
\end{itemize} 
\vspace*{-\baselineskip}

\textbf{Vandenberg Air Force Base} 
\hfill June 2011 -- December 2011 \\ 
Lompoc, CA
\begin{itemize}\itemsep -2pt
\item Characterized ground-based sensors for Space Situational Awareness group.
\item Began development of a program to make observation abilities apparent to new users.
\end{itemize}
\vspace*{-\baselineskip}

\textbf{Information Sciences Institute (ISI)} \hfill May 2009 -- April 2012 \\
Space Engineering Research Center, Marina del Rey 
\begin{itemize}\itemsep -2pt
\item Was part of the team that helped to create the Caerus portion of the Mayflower-Caerus 3U CubeSat and the Aeneas CubeSat.
\item Team lead for LEAPFROG lunar lander avionics group.
\end{itemize}
\vspace*{-\baselineskip}
%----------------------------------------------------------------------------------------

\section{POSTGRADUATE RESEARCH}
\textbf{MSc Research}
\begin{itemize} \itemsep -2pt
\item Built an autonomous powered glider to take atmospheric data for wind farm optimization.
\item Utilized Gaussian processes to predict local, small-scale weather patterns.
\item Designed to fill in for relatively low resolution satellite and weather station data.
\end{itemize}
\vspace*{-\baselineskip}

\textbf{PhD Research}
\begin{itemize} \itemsep -2pt
\item Considerable experience working with the Raytrix R5 camera and accompanying Raytrix Software
\item Used deep learning to enhance extreme low light images. Paper submitted to ICCP 2019, pending review.
\item Collected light fields using PR2 and Baxter robots in a spherical parameterization. 
\item Built several custom light field rendering engines.
\end{itemize}
\vspace*{-\baselineskip}

\textbf{TA Positions}
\begin{itemize} \itemsep -2pt
\item Two years of overseeing student groups in the UoE \emph{System Design Project} under Barbara Webb.
\item One year as TA for \emph{Embedded Systems} at HW under Sen Wang
\item At time of writing, preparing for \emph{Computer Architecture} course run by Alexander Belyaev.
\end{itemize}
\vspace*{-\baselineskip}

\section{TECHNICAL SKILLS}
\begin{itemize} \itemsep -2pt
\item Proficient in: C++, SolidWorks, MATLAB, Keras/TensorFlow, Robot Operating System (ROS), Python, OpenCV, Raytrix API, Light Field Toolbox, electronics (including soldering, assembly, measuring etc), RC Piloting.
\item Working Knowledge of: XFoil, composites, ActionScript, deep learning.
\end{itemize}
\vspace*{-\baselineskip}

\section{GENERAL INTERESTS}
\begin{itemize} \itemsep -2pt
\item Avid drone racer and exploratory drone creator/operator, both fixed wing and multirotor. 
\item Constructed an automated greenhouse indoors using RPI and Arduino.
\item Dedicated off-roader, expeditioner, and overlander, be it by Jeep or fat bike.
\item Grew up riding horses and took up polo while living in Edinburgh. etc...
\end{itemize}

%----------------------------------------------------------------------------------------

\end{resume} 
\end{document}